Galois Slicing as Automatic Differentiation

### 2025-07-11 main/approx-as-tangents.tex
Lose paragraph break inside enum.

  \item The $\mathrm{gustave}$ function is stable. Despite there being
    no one minimal input that achieves the output $\top$, each of the
    minimal inputs that can achieve this output are pairwise
    incomparable, so for each specific input that gets output $\top$
    there is a unique minimal input that achieves it (listed in the
    first three lines of the definition).

    In terms of \GPS the $\mathrm{gustave}$ function does not present
    a problem. For any particular run (i.e., input $\mapsto$ output
    pair), there is an unambiguous minimal input that achieves the
    output, no matter that it was not achieved by a sequential
    processing of the input.

>>>>

  \item The $\mathrm{gustave}$ function is stable. Despite there being
    no one minimal input that achieves the output $\top$, each of the
    minimal inputs that can achieve this output are pairwise
    incomparable, so for each specific input that gets output $\top$
    there is a unique minimal input that achieves it (listed in the
    first three lines of the definition). %
%
    In terms of \GPS, the $\mathrm{gustave}$ function does not present
    a problem; for any particular run (i.e., input $\mapsto$ output
    pair), there is an unambiguous minimal input that achieves the
    output, no matter that it was not achieved by a sequential
    processing of the input.
